LHC abort gap monitor electronics upgrade

### 2024-03-18 paper.tex
added descriptions for ai
generated pictures added to the paper
created table for comparison of the two systems
added new pictures in the paper

\section{Current system design}
        %description of the system
        %Utilization of Analogue Integrator ASIC
        %40 MHz Analogue-to-Digital Converter (ADC)
        %Operation Since 2010
        %Reasons for Obsolescence
        %Digital Signal Processing Approach why and outcomes
    \subsection{Technical Solution}
        %Utilization of Analogue Integrator ASIC
        %40 MHz Analogue-to-Digital Converter (ADC)
        %Operation Since 2010
        %Reasons for Obsolescence
        %Digital Signal Processing Approach why and outcomes

\section{New fully digitized AGM}
    \subsection{}

\section{Comparison of Implementations}
    %compare the changes and comment the expected changes

@@

\section{Discussion}
    \subsection{Significance of the Upgrade}
    \subsection{Future Implications}
    % \subsubsection{Potential for Further Enhancements or Modifications}
    % \subsubsection{Integration with Other Accelerator Technologies}

\section{Conclusion}
\section{Acknowledgments}

>>>>

% lhc works with high energy beam which is strong enought to cause damage to
% the machine beam bunch train has abort gap at the last bunch slots creating a
% time gap of 3us this place should be empty because particles in this gap
% don't get enough thrust to be directed towards the beam dumps and so they hit
% hit the magnets controling the beam, which can cause quenching in the magnets
% and losing the control over the beam. 
% The Abort Gap monitor serves to continuously monitor amount of particles in
% abort gap and gives the information to start the abort gap cleaning process.

\section{system architecture}
basic methodology how to monitor this area is to exploit the synchrotron
radiation light (SL). This phenomena appears when a particle is moving on a
circular trajectory. The energy of the beam is proportional to the changes in
the radiated spectrum. With increasing energy, the light is shifted towards
shorter wavelengths. Since the LHC works with the energy from 
\begin{figure}[!tbh]
    \centering
    \includegraphics[width=\columnwidth]{bsra_chain.pdf}
    \caption{BSRA Chain}
    \label{fig:bsra_chain}
\end{figure}

\subsection{Technical Solution}
        %Utilization of Analogue Integrator ASIC
        %40 MHz Analogue-to-Digital Converter (ADC)
        %Operation Since 2010
        %Reasons for Obsolescence
        %Digital Signal Processing Approach why and outcomes

        \begin{figure}[!tbh]
            \centering
            \includegraphics[width=\columnwidth]{bsra_daq.pdf}
            \caption{upgraded amplifier}
            \label{fig:amplifier}
        \end{figure}

\section{New fully digitized AGM}

        \begin{figure}[!tbh]
            \centering
            \includegraphics[width=\columnwidth]{amp_schematics.pdf}
            \caption{upgraded amplifier}
            \label{fig:amplifier}
        \end{figure}

% \section{Comparison of Implementations}
%     \input{tables/system_comparison.tex} 
%     %compare the changes and comment the expected changes

@@

    \begin{figure}[!htb]
      \begin{center}
          \scalebox{0.54}{\input{plots/ions.pgf}}
          \caption{Comparison of AGMs}
          \label{fig:comparison_chart}
      \end{center}
    \end{figure}

% \section{Discussion}
%     \subsection{Significance of the Upgrade}
%     \subsection{Future Implications}
%     % \subsubsection{Potential for Further Enhancements or Modifications}
%     % \subsubsection{Integration with Other Accelerator Technologies}

\section{Conclusion}
